Assumptions of Physics blueprint: information granularity as a common foundation for geometry, measures and probability

### 2021-12-09 Overviews/Informational granularity/InformationGranularity.tex
ImformationGranularity: added another example

\section{Spaces we need to be able to capture}

>>>>

\subsection{Example of lack of equigranular or comparable possibilities}

Consider the case of a balanced die. It will have six equigranular possibilities. Consider the case of an unbalanced die. It will have six possibilities, but they will not be equigranular. Consider the case where you may have a balanced or unbalanced die. It is not clear whether these cases should be equigranular or not. Therefore we should leave that as not comparable. In this case, the possibilities are twelve divided into two groups. Two possibilities with the group will be comparable but not across groups.

\subsection{Spaces we need to be able to capture}
